A template for writing a manuscript in Rmarkdown

### 2018-09-21 manuscript/manuscript_template.tex
Updating Rmarkdown template

<!DOCTYPE html>
<html lang="en">
  <head>
    <meta charset="utf-8">
  <link rel="dns-prefetch" href="https://assets-cdn.github.com">
  <link rel="dns-prefetch" href="https://avatars0.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars1.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars2.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars3.githubusercontent.com">
  <link rel="dns-prefetch" href="https://github-cloud.s3.amazonaws.com">
  <link rel="dns-prefetch" href="https://user-images.githubusercontent.com/">

  <link crossorigin="anonymous" media="all" integrity="sha512-/yZA7MGD9acBi5MmgjnivwjGeiNsmimsI/bhLlK7akrRuw+hMxNpJoQEMO9Zt0Nq6ZRu1m1NGV6r95Ib0zx7Qw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/frameworks-1ca00d32d1a8adc78ae7bb6677410eb1.css" />
  <link crossorigin="anonymous" media="all" integrity="sha512-pHF1luoMSUFxvz63bW3jEbbifYl/pruHUw+kljThAPi2g0nhgMdvWj4bQRh4O8MYp9NR60XYcylaLXmYA8YXSw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/github-5043b3d96d50b119b971c2cdde4e0a62.css" />

  <meta name="viewport" content="width=device-width">

  <title>Blog/manuscript_template.tex at master · petrkeil/Blog</title>
    <meta name="description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog">
    <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub">
  <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub">
  <meta property="fb:app_id" content="1401488693436528">

    <meta property="og:image" content="https://avatars2.githubusercontent.com/u/5421227?s=400&amp;v=4" /><meta property="og:site_name" content="GitHub" /><meta property="og:type" content="object" /><meta property="og:title" content="petrkeil/Blog" /><meta property="og:url" content="https://github.com/petrkeil/Blog" /><meta property="og:description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog" />

  <link rel="assets" href="https://assets-cdn.github.com/">
  <link rel="web-socket" href="wss://live.github.com/_sockets/VjI6MzE5MjkzMDMyOjcxODYyYzE1ZGViNTZjN2U2YjQzMjlhZWYzYzI0Mjk2MjFjODZlN2QzMzM0YmVkYzI2NWJhNDYyY2JkYjc2MTM=--6f13a55f6f2aea699ea77deb92d45357f788dd6a">
  <meta name="pjax-timeout" content="1000">
  <link rel="sudo-modal" href="/sessions/sudo_modal">
  <meta name="request-id" content="DECF:7B7C:B3E55E:147C953:5BA52F75" data-pjax-transient>

  <meta name="selected-link" value="repo_source" data-pjax-transient>

      <meta name="google-site-verification" content="KT5gs8h0wvaagLKAVWq8bbeNwnZZK1r1XQysX3xurLU">
    <meta name="google-site-verification" content="ZzhVyEFwb7w3e0-uOTltm8Jsck2F5StVihD0exw2fsA">
    <meta name="google-site-verification" content="GXs5KoUUkNCoaAZn7wPN-t01Pywp9M3sEjnt_3_ZWPc">

  <meta name="octolytics-host" content="collector.githubapp.com" /><meta name="octolytics-app-id" content="github" /><meta name="octolytics-event-url" content="https://collector.githubapp.com/github-external/browser_event" /><meta name="octolytics-dimension-request_id" content="DECF:7B7C:B3E55E:147C953:5BA52F75" /><meta name="octolytics-dimension-region_edge" content="iad" /><meta name="octolytics-dimension-region_render" content="iad" /><meta name="octolytics-actor-id" content="34245401" /><meta name="octolytics-actor-login" content="jamesgrecian" /><meta name="octolytics-actor-hash" content="821728246d06cdfe784e56dfb8dc2a4447ec5ee2fb7525c8728616156ffa29a2" />
<meta name="analytics-location" content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" />

    <meta name="google-analytics" content="UA-3769691-2">

  <meta class="js-ga-set" name="userId" content="078bbd73f63945865b3a6f9e3c674706" %>

<meta class="js-ga-set" name="dimension1" content="Logged In">

      <meta name="hostname" content="github.com">
    <meta name="user-login" content="jamesgrecian">

      <meta name="expected-hostname" content="github.com">
    <meta name="js-proxy-site-detection-payload" content="ZjQ2OTM3ZjcwZjc1MzhhMTAyNTFmYmY2MDk5NmJjYjZlM2NjNmMwMmQwYjExOTc1NGVlZDU4YzMzMzBkYmNhNXx7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjM0LjI0OC4yMDciLCJyZXF1ZXN0X2lkIjoiREVDRjo3QjdDOkIzRTU1RToxNDdDOTUzOjVCQTUyRjc1IiwidGltZXN0YW1wIjoxNTM3NTUyMjQ2LCJob3N0IjoiZ2l0aHViLmNvbSJ9">

    <meta name="enabled-features" content="DASHBOARD_V2_LAYOUT_OPT_IN,EXPLORE_DISCOVER_REPOSITORIES,UNIVERSE_BANNER,MARKETPLACE_PLAN_RESTRICTION_EDITOR,MARKETPLACE_RETARGETING,QUOTE_MARKDOWN">

  <meta name="html-safe-nonce" content="4d33eb369dbc9e939c0c70269799ff90a62c9762">

  <meta http-equiv="x-pjax-version" content="3842ef7af97baac02526bd1bb609fd99">

      <link href="https://github.com/petrkeil/Blog/commits/master.atom" rel="alternate" title="Recent Commits to Blog:master" type="application/atom+xml">

  <meta name="go-import" content="github.com/petrkeil/Blog git https://github.com/petrkeil/Blog.git">

  <meta name="octolytics-dimension-user_id" content="5421227" /><meta name="octolytics-dimension-user_login" content="petrkeil" /><meta name="octolytics-dimension-repository_id" content="32012442" /><meta name="octolytics-dimension-repository_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_public" content="true" /><meta name="octolytics-dimension-repository_is_fork" content="false" /><meta name="octolytics-dimension-repository_network_root_id" content="32012442" /><meta name="octolytics-dimension-repository_network_root_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_explore_github_marketplace_ci_cta_shown" content="false" />

    <link rel="canonical" href="https://github.com/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.tex" data-pjax-transient>

  <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">

  <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">

  <link rel="mask-icon" href="https://assets-cdn.github.com/pinned-octocat.svg" color="#000000">
  <link rel="icon" type="image/x-icon" class="js-site-favicon" href="https://assets-cdn.github.com/favicon.ico">

<meta name="theme-color" content="#1e2327">

  <link rel="manifest" href="/manifest.json" crossOrigin="use-credentials">

  </head>

  <body class="logged-in env-production page-blob">

  <div class="position-relative js-header-wrapper ">
    <a href="#start-of-content" tabindex="1" class="p-3 bg-blue text-white show-on-focus js-skip-to-content">Skip to content</a>
    <div id="js-pjax-loader-bar" class="pjax-loader-bar"><div class="progress"></div></div>

<header class="Header  f5" role="banner">
  <div class="d-flex flex-justify-between px-3 ">
    <div class="d-flex flex-justify-between ">
      <div class="">
        <a class="header-logo-invertocat" href="https://github.com/" data-hotkey="g d" aria-label="Homepage" data-ga-click="Header, go to dashboard, icon:logo">
  <svg height="32" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="32" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
</a>

      </div>

    </div>

    <div class="HeaderMenu d-flex flex-justify-between flex-auto">
      <div class="d-flex">
            <div class="">
              <div class="header-search scoped-search site-scoped-search js-site-search position-relative js-jump-to"
  role="combobox"
  aria-owns="jump-to-results"
  aria-label="Search or jump to"
  aria-haspopup="listbox"
  aria-expanded="false"
>
  <div class="position-relative">
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-site-search-form" data-scope-type="Repository" data-scope-id="32012442" data-scoped-search-url="/petrkeil/Blog/search" data-unscoped-search-url="/search" action="/petrkeil/Blog/search" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
      <label class="form-control header-search-wrapper header-search-wrapper-jump-to position-relative d-flex flex-justify-between flex-items-center js-chromeless-input-container">
        <input type="text"
          class="form-control header-search-input jump-to-field js-jump-to-field js-site-search-focus js-site-search-field is-clearable"
          data-hotkey="s,/"
          name="q"
          value=""
          placeholder="Search or jump to…"
          data-unscoped-placeholder="Search or jump to…"
          data-scoped-placeholder="Search or jump to…"
          autocapitalize="off"
          aria-autocomplete="list"
          aria-controls="jump-to-results"
          data-jump-to-suggestions-path="/_graphql/GetSuggestedNavigationDestinations#csrf-token=zcJUvtqaKw72uX3+FzR9OQAX21rWJn+bojDj6/4pZ0qqkkAAzhaUHBTvUq9jh6W93uzACkd2Vi0N1v0kqc+Jpw=="
          spellcheck="false"
          autocomplete="off"
          >
          <input type="hidden" class="js-site-search-type-field" name="type" >
            <img src="https://assets-cdn.github.com/images/search-shortcut-hint.svg" alt="" class="mr-2 header-search-key-slash">

            <div class="Box position-absolute overflow-hidden d-none jump-to-suggestions js-jump-to-suggestions-container">
              <ul class="d-none js-jump-to-suggestions-template-container">
                <li class="d-flex flex-justify-start flex-items-center p-0 f5 navigation-item js-navigation-item" role="option">
                  <a tabindex="-1" class="no-underline d-flex flex-auto flex-items-center p-2 jump-to-suggestions-path js-jump-to-suggestion-path js-navigation-open" href="">
                    <div class="jump-to-octicon js-jump-to-octicon mr-2 text-center d-none">
                      <svg height="16" width="16" class="octicon octicon-repo flex-shrink-0 js-jump-to-octicon-repo d-none" title="Repository" aria-label="Repository" viewBox="0 0 12 16" version="1.1" role="img"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
                      <svg height="16" width="16" class="octicon octicon-project flex-shrink-0 js-jump-to-octicon-project d-none" title="Project" aria-label="Project" viewBox="0 0 15 16" version="1.1" role="img"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
                      <svg height="16" width="16" class="octicon octicon-search flex-shrink-0 js-jump-to-octicon-search d-none" title="Search" aria-label="Search" viewBox="0 0 16 16" version="1.1" role="img"><path fill-rule="evenodd" d="M15.7 13.3l-3.81-3.83A5.93 5.93 0 0 0 13 6c0-3.31-2.69-6-6-6S1 2.69 1 6s2.69 6 6 6c1.3 0 2.48-.41 3.47-1.11l3.83 3.81c.19.2.45.3.7.3.25 0 .52-.09.7-.3a.996.996 0 0 0 0-1.41v.01zM7 10.7c-2.59 0-4.7-2.11-4.7-4.7 0-2.59 2.11-4.7 4.7-4.7 2.59 0 4.7 2.11 4.7 4.7 0 2.59-2.11 4.7-4.7 4.7z"/></svg>
                    </div>

                    <img class="avatar mr-2 flex-shrink-0 js-jump-to-suggestion-avatar d-none" alt="" aria-label="Team" src="" width="28" height="28">

                    <div class="jump-to-suggestion-name js-jump-to-suggestion-name flex-auto overflow-hidden text-left no-wrap css-truncate css-truncate-target">
                    </div>

                    <div class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none js-jump-to-badge-search">
                      <span class="js-jump-to-badge-search-text-default d-none" aria-label="in this repository">
                        In this repository
                      </span>
                      <span class="js-jump-to-badge-search-text-global d-none" aria-label="in all of GitHub">
                        All GitHub
                      </span>
                      <span aria-hidden="true" class="d-inline-block ml-1 v-align-middle">↵</span>
                    </div>

                    <div aria-hidden="true" class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none d-on-nav-focus js-jump-to-badge-jump">
                      Jump to
                      <span class="d-inline-block ml-1 v-align-middle">↵</span>
                    </div>
                  </a>
                </li>
              </ul>
              <ul class="d-none js-jump-to-no-results-template-container">
                <li class="d-flex flex-justify-center flex-items-center p-3 f5 d-none">
                  <span class="text-gray">No suggested jump to results</span>
                </li>
              </ul>

              <ul id="jump-to-results" role="listbox" class="js-navigation-container jump-to-suggestions-results-container js-jump-to-suggestions-results-container" >
                <li class="d-flex flex-justify-center flex-items-center p-0 f5">
                  <img src="https://assets-cdn.github.com/images/spinners/octocat-spinner-128.gif" alt="Octocat Spinner Icon" class="m-2" width="28">
                </li>
              </ul>
            </div>
      </label>
</form>  </div>
</div>

            </div>

          <ul class="d-flex pl-2 flex-items-center text-bold list-style-none" role="navigation">
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g p" data-ga-click="Header, click, Nav menu - item:pulls context:user" aria-label="Pull requests you created" data-selected-links="/pulls /pulls/assigned /pulls/mentioned /pulls" href="/pulls">
                Pull requests
</a>            </li>
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g i" data-ga-click="Header, click, Nav menu - item:issues context:user" aria-label="Issues you created" data-selected-links="/issues /issues/assigned /issues/mentioned /issues" href="/issues">
                Issues
</a>            </li>
              <li>
                <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:marketplace context:user" data-octo-click="marketplace_click" data-octo-dimensions="location:nav_bar" data-selected-links=" /marketplace" href="/marketplace">
                   Marketplace
</a>              </li>
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:explore" data-selected-links="/explore /trending /trending/developers /integrations /integrations/feature/code /integrations/feature/collaborate /integrations/feature/ship showcases showcases_search showcases_landing /explore" href="/explore">
                Explore
</a>            </li>
          </ul>
      </div>

      <div class="d-flex">

<ul class="user-nav d-flex flex-items-center list-style-none" id="user-links">
  <li class="dropdown">
    <span class="d-inline-block  px-2">

    <a aria-label="You have no unread notifications" class="notification-indicator tooltipped tooltipped-s  js-socket-channel js-notification-indicator" data-hotkey="g n" data-ga-click="Header, go to notifications, icon:read" data-channel="notification-changed:34245401" href="/notifications">
        <span class="mail-status "></span>
        <svg class="octicon octicon-bell" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M13.99 11.991v1H0v-1l.73-.58c.769-.769.809-2.547 1.189-4.416.77-3.767 4.077-4.996 4.077-4.996 0-.55.45-1 .999-1 .55 0 1 .45 1 1 0 0 3.387 1.229 4.156 4.996.38 1.879.42 3.657 1.19 4.417l.659.58h-.01zM6.995 15.99c1.11 0 1.999-.89 1.999-1.999H4.996c0 1.11.89 1.999 1.999 1.999z"/></svg>
</a>
    </span>
  </li>

  <li class="dropdown">
    <details class="details-overlay details-reset d-flex px-2 flex-items-center">
      <summary class="HeaderNavlink"
         aria-label="Create new…"
         data-ga-click="Header, create new, icon:add">
        <svg class="octicon octicon-plus float-left mr-1 mt-1" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 9H7v5H5V9H0V7h5V2h2v5h5v2z"/></svg>
        <span class="dropdown-caret mt-1"></span>
      </summary>
      <details-menu class="dropdown-menu dropdown-menu-sw">

<a role="menuitem" class="dropdown-item" href="/new" data-ga-click="Header, create new repository">
  New repository
</a>

  <a role="menuitem" class="dropdown-item" href="/new/import" data-ga-click="Header, import a repository">
    Import repository
  </a>

<a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, create new gist">
  New gist
</a>

  <a role="menuitem" class="dropdown-item" href="/organizations/new" data-ga-click="Header, create new organization">
    New organization
  </a>

  <div class="dropdown-divider"></div>
  <div class="dropdown-header">
    <span title="petrkeil/Blog">This repository</span>
  </div>
    <a role="menuitem" class="dropdown-item" href="/petrkeil/Blog/issues/new" data-ga-click="Header, create new issue">
      New issue
    </a>

      </details-menu>
    </details>
  </li>

  <li class="dropdown">

    <details class="details-overlay details-reset d-flex pl-2 flex-items-center">
      <summary class="HeaderNavlink name mt-1"
        aria-label="View profile and more"
        data-ga-click="Header, show menu, icon:avatar">
        <img alt="@jamesgrecian" class="avatar float-left mr-1" src="https://avatars2.githubusercontent.com/u/34245401?s=40&amp;v=4" height="20" width="20">
        <span class="dropdown-caret"></span>
      </summary>
      <details-menu class="dropdown-menu dropdown-menu-sw">
        <ul>
          <li class="header-nav-current-user css-truncate"><a role="menuitem" class="no-underline user-profile-link px-3 pt-2 pb-2 mb-n2 mt-n1 d-block" href="/jamesgrecian" data-ga-click="Header, go to profile, text:Signed in as">Signed in as <strong class="css-truncate-target">jamesgrecian</strong></a></li>
          <li class="dropdown-divider"></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian" data-ga-click="Header, go to profile, text:your profile">Your profile</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=repositories" data-ga-click="Header, go to repositories, text:your repositories">Your repositories</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=stars" data-ga-click="Header, go to starred repos, text:your stars">Your stars</a></li>
            <li><a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, your gists, text:your gists">Your gists</a></li>
          <li class="dropdown-divider"></li>
          <li><a role="menuitem" class="dropdown-item" href="https://help.github.com" data-ga-click="Header, go to help, text:help">Help</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/settings/profile" data-ga-click="Header, go to settings, icon:settings">Settings</a></li>
          <li>
            <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="logout-form" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="OM5YtlFU+S06U7ppNLcVxzqWiaBef+wxiPcpMrVBU5MT4j+3rc/PsPef/kanszc+s9gxETZMWv4UhgAFQxQtTA==" />
              <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout" role="menuitem">
                Sign out
              </button>
</form>          </li>
        </ul>
      </details-menu>
    </details>
  </li>
</ul>

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="sr-only right-0" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="N1zKEjZbcCo1MI7p6SB0skpuMDcaIk1EZ0F9bAHxVPkccK0TysBGt/j8ysZ6JFZLwyCIhnIR+4v7MFRb96QqJg==" />
          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
            Sign out
          </button>
</form>      </div>
    </div>
  </div>
</header>

  </div>

  <div id="start-of-content" class="show-on-focus"></div>

    <div id="js-flash-container">

</div>

  <div role="main" class="application-main ">
        <div itemscope itemtype="http://schema.org/SoftwareSourceCode" class="">
    <div id="js-repo-pjax-container" data-pjax-container >

  <div class="pagehead repohead instapaper_ignore readability-menu experiment-repo-nav  ">
    <div class="repohead-details-container clearfix container">

      <ul class="pagehead-actions">
  <li>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form data-autosubmit="true" data-remote="true" class="js-social-container" action="/notifications/subscribe" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="waV7OqLCkNQ0PEw4EE9fOf24fp4CwT8NUr+psybqPnPC2pmp6iqyjyCcpVUE5PcRzsja2lcTlEgrF7iTkvBrEw==" />      <input type="hidden" name="repository_id" id="repository_id" value="32012442" class="form-control" />

        <div class="select-menu js-menu-container js-select-menu">
          <a href="/petrkeil/Blog/subscription"
            class="btn btn-sm btn-with-count select-menu-button js-menu-target"
            role="button"
            aria-haspopup="true"
            aria-expanded="false"
            aria-label="Toggle repository notifications menu"
            data-ga-click="Repository, click Watch settings, action:blob#show">
            <span class="js-select-button">
                <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
                Watch
            </span>
          </a>
          <a class="social-count js-social-count"
            href="/petrkeil/Blog/watchers"
            aria-label="17 users are watching this repository">
            17
          </a>

        <div class="select-menu-modal-holder">
          <div class="select-menu-modal subscription-menu-modal js-menu-content">
            <div class="select-menu-header js-navigation-enable" tabindex="-1">
              <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
              <span class="select-menu-title">Notifications</span>
            </div>

              <div class="select-menu-list js-navigation-container" role="menu">

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={A template for writing a manuscript in Rmarkdown},
            pdfauthor={James Grecian One; Ian Jonsen Two},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{A template for writing a manuscript in Rmarkdown}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{James Grecian One\footnote{University of Somewhere} \\ Ian Jonsen Two\footnote{University of Nowhere}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{21 September 2018}

\usepackage{lineno}
\linenumbers

\begin{document}
\maketitle

\section{Abstract}\label{abstract}

\emph{Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel
erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet
argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
liberavisse sea. Ponderum vivendum te nec, id agam brute disputando
mei.}

\section{Introduction}\label{introduction}

Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat
falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum
suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
conceptam.

Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
percipitur at vis. Numquam similique in per, te quo saepe utroque
pericula.

Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
suas latine vix, eos oblique sanctus pertinax cu.

\section{Methods}\label{methods}

Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat
falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum
suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
conceptam.

\subsection{Equations}\label{equations}

The deterministic part of the model is defined by this \textbf{in-line
equation} as \(\mu_i = \beta_0 + \beta_1x\), and the stochastic part by
the \textbf{centered equation}:

\[ \frac{1}{\sqrt{2\pi}\sigma}e^{-(x-\mu_i)^2/(2\sigma^2)} \]

\subsection{Tables}\label{tables}

\begin{longtable}[]{@{}lrrrr@{}}
\caption{This is a GLM summary table.}\tabularnewline
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endfirsthead
\toprule
& Estimate & Std. Error & t value &
Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
\midrule
\endhead
(Intercept) & 0.05 & 0.1 & 0.48 & 0.63\tabularnewline
x & 1.96 & 0.1 & 19.68 & 0.00\tabularnewline
\bottomrule
\end{longtable}

\subsection{Plots}\label{plots}

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_template_files/figure-latex/carDataPlot-1.pdf}
\caption{Relationship between x and y. The solid line is least-squares
linear regression.}
\end{figure}

\subsection{Citations}\label{citations}

The relationship was first described by @Halpern\_2006. However, there
are also opinions that the relationship is spurious {[}@Keil\_2012{]}.
We used R for our calculations {[}@R\_Core\_Team\_2017{]}, and we used
package \texttt{knitcitations} {[}@Boettiger\_2017{]} to make the
bibliography.

\section{Results and discussion}\label{results-and-discussion}

Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat
falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum
suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.

Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
conceptam.

Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
percipitur at vis. Numquam similique in per, te quo saepe utroque
pericula.

Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
suas latine vix, eos oblique sanctus pertinax cu.

\section{References}\label{references}

\end{document}
